\begin{thebibliography}{99}
	
	\bibitem{han2024classification}
	H.~Han et~al., ``Classification and automatic scoring of arousal intensity during sleep stages using machine learning,'' \emph{Scientific Reports}, vol.~14, no.~1, Dec. 2024, doi: \href{https://doi.org/10.1038/s41598-023-50653-9}{10.1038/s41598-023-50653-9}.
	
	\bibitem{tsinalis2016automatic}
	O.~Tsinalis et~al., ``Automatic Sleep Stage Scoring Using Time-Frequency Analysis and Stacked Sparse Autoencoders,'' \emph{Annals of Biomedical Engineering}, vol.~44, no.~5, May 2016, doi: \href{https://doi.org/10.1007/s10439-015-1444-y}{10.1007/s10439-015-1444-y}.
	
	\bibitem{krakovska2011automatic}
	A.~Krakovsk치 and K.~Mezeiov치, ``Automatic sleep scoring: A search for an optimal combination of measures,'' \emph{Artificial Intelligence in Medicine}, vol.~53, no.~1, Sep. 2011, doi: \href{https://doi.org/10.1016/j.artmed.2011.06.004}{10.1016/j.artmed.2011.06.004}.
	
	\bibitem{biswal2018expert}
	S.~Biswal et~al., ``Expert-level sleep scoring with deep neural networks,'' \emph{Journal of the American Medical Informatics Association}, vol.~25, no.~12, Dec. 2018, doi: \href{https://doi.org/10.1093/jamia/ocy131}{10.1093/jamia/ocy131}.
	
	\bibitem{ronzhina2012sleep}
	M.~Ronzhina et~al., ``Sleep scoring using artificial neural networks,'' \emph{Sleep Medicine Reviews}, vol.~16, no.~3, Jun. 2012, doi: \href{https://doi.org/10.1016/j.smrv.2011.06.003}{10.1016/j.smrv.2011.06.003}.
	
	\bibitem{alsolai2022systematic}
	H.~Alsolai et~al., ``A Systematic Review of Literature on Automated Sleep Scoring,'' \emph{IEEE Access}, vol.~10, pp.~79419--79443, 2022, doi: \href{https://doi.org/10.1109/ACCESS.2022.3194145}{10.1109/ACCESS.2022.3194145}.
	
	\bibitem{fiorillo2019automated}
	L.~Fiorillo et~al., ``Automated sleep scoring: A review of the latest approaches,'' \emph{Sleep Medicine Reviews}, vol.~48, Dec. 2019, doi: \href{https://doi.org/10.1016/j.smrv.2019.07.007}{10.1016/j.smrv.2019.07.007}.
	
	\bibitem{faust2019review}
	O.~Faust et~al., ``A review of automated sleep stage scoring based on physiological signals for the new millennia,'' \emph{Computer Methods and Programs in Biomedicine}, vol.~176, Jul. 2019, doi: \href{https://doi.org/10.1016/j.cmpb.2019.04.032}{10.1016/j.cmpb.2019.04.032}.
	
	\bibitem{chriskos2021review}
	P.~Chriskos et~al., ``A review on current trends in automatic sleep staging through bio-signal recordings and future challenges,'' \emph{Sleep Medicine Reviews}, vol.~55, Feb. 2021, doi: \href{https://doi.org/10.1016/j.smrv.2020.101377}{10.1016/j.smrv.2020.101377}.
	
	\bibitem{phan2022sleeptransformer}
	H.~Phan, K.~B. Mikkelsen, O.~Y. Chen, P.~Koch, A.~Mertins, and M.~De~Vos, ``SleepTransformer: Automatic Sleep Staging with Interpretability and Uncertainty Quantification,'' \emph{IEEE Transactions on Biomedical Engineering}, 2022.
	
	

	
	\bibitem{han2024classification}
	H.~Han et~al., ``Classification and automatic scoring of arousal intensity during sleep stages using machine learning,'' \emph{Scientific Reports}, vol.~14, no.~1, Dec. 2024.
	
	\bibitem{tsinalis2016automatic}
	O.~Tsinalis et~al., ``Automatic Sleep Stage Scoring Using Time-Frequency Analysis and Stacked Sparse Autoencoders,'' \emph{Annals of Biomedical Engineering}, vol.~44, no.~5, May 2016.
	
	\bibitem{krakovska2011automatic}
	A.~Krakovsk치 and K.~Mezeiov치, ``Automatic sleep scoring: A search for an optimal combination of measures,'' \emph{Artificial Intelligence in Medicine}, vol.~53, no.~1, Sep. 2011.
	
	\bibitem{biswal2018expert}
	S.~Biswal et~al., ``Expert-level sleep scoring with deep neural networks,'' \emph{JAMIA}, vol.~25, no.~12, Dec. 2018.
	
	\bibitem{ronzhina2012sleep}
	M.~Ronzhina et~al., ``Sleep scoring using artificial neural networks,'' \emph{Sleep Medicine Reviews}, vol.~16, no.~3, Jun. 2012.
	
	\bibitem{alsolai2022systematic}
	H.~Alsolai et~al., ``A Systematic Review of Literature on Automated Sleep Scoring,'' \emph{IEEE Access}, vol.~10, 2022.
	
	\bibitem{fiorillo2019automated}
	L.~Fiorillo et~al., ``Automated sleep scoring: A review of the latest approaches,'' \emph{Sleep Medicine Reviews}, vol.~48, Dec. 2019.
	
	\bibitem{faust2019review}
	O.~Faust et~al., ``A review of automated sleep stage scoring based on physiological signals for the new millennia,'' \emph{Computer Methods and Programs in Biomedicine}, vol.~176, Jul. 2019.
	
	\bibitem{chriskos2021review}
	P.~Chriskos et~al., ``A review on current trends in automatic sleep staging through bio-signal recordings and future challenges,'' \emph{Sleep Medicine Reviews}, vol.~55, Feb. 2021.
	
	\bibitem{phan2022sleeptransformer}
	H.~Phan et~al., ``SleepTransformer: Automatic Sleep Staging with Interpretability and Uncertainty Quantification,'' \emph{IEEE Transactions on Biomedical Engineering}, 2022.
	
	\bibitem{dai2023multichannelsleepnet}
	Y.~Dai et~al., ``MultiChannelSleepNet: A Transformer-Based Model for Automatic Sleep Stage Classification With PSG,'' \emph{IEEE J. Biomed. Health Inform.}, 2023.
	
	\bibitem{guo2024flexsleeptransformer}
	Y.~Guo, M.~Nowakowski, and W.~Dai, ``FlexSleepTransformer: A Transformer-Based Sleep Staging Model with Flexible Input Channel Configurations,'' \emph{Scientific Reports}, 2024.
	
	\bibitem{yao2022cnntransformer}
	Z.~Yao and X.~Liu, ``A CNN-Transformer Deep Learning Model for Real-time Sleep Stage Classification in an Energy-Constrained Wireless Device,'' \emph{medRxiv}, 2022.
	
	\bibitem{supratak2017deepsleepnet}
	A.~Supratak et~al., ``DeepSleepNet: A Model for Automatic Sleep Stage Scoring Based on Raw Single-Channel EEG,'' \emph{IEEE Trans. Neural Syst. Rehabil. Eng.}, vol.~25, no.~11, pp.~1998--2008, 2017.
	
	\bibitem{eldele2021attnsleep}
	E.~Eldele et~al., ``AttnSleep: An Attention-Based Deep Learning Approach for Sleep Stage Classification With Single-Channel EEG,'' \emph{IEEE Trans. Neural Syst. Rehabil. Eng.}, 2021.
	
	\bibitem{ji2022jkstgcn}
	X.~Ji, Y.~Li, and P.~Wen, ``Jumping Knowledge-Based Spatial-Temporal Graph Convolutional Networks for Automatic Sleep Stage Classification,'' \emph{IEEE Trans. Neural Syst. Rehabil. Eng.}, 2022.
	
	\bibitem{mousavi2019sleepeegnet}
	S.~Mousavi, F.~Afghah, and U.~R. Acharya, ``SleepEEGNet: Automated Sleep Stage Scoring With Sequence-to-Sequence Deep Learning Approach,'' \emph{PLOS ONE}, 2019.
	
	\bibitem{phan2019seqsleepnet}
	H.~Phan et~al., ``SeqSleepNet: End-to-End Hierarchical Recurrent Neural Network for Sequence-to-Sequence Automatic Sleep Staging,'' \emph{IEEE Trans. Neural Syst. Rehabil. Eng.}, 2019.
	
	\bibitem{zhang2024cnntransformerconvlstm}
	Zhang et~al., ``A CNN-Transformer-ConvLSTM-CRF Hybrid Network for Sleep Stage Classification,'' \emph{IEEE Sensors Journal}, 2024.
	
	\bibitem{liu2024review}
	Liu et~al., ``Automatic Sleep Stage Classification Using Deep Learning: Signals, Data Representation, and Neural Networks,'' \emph{Artificial Intelligence Review}, 2024.
	
	\bibitem{ctdal2022}
	CT-DAL, ``Convolutional Transformer with Domain Adversarial Learning for Multi-Channel Sleep Stage Classification,'' \emph{Available on Semantic Scholar}, 2022.
	
	\bibitem{pei2022hybrid}
	W.~Pei, Y.~Li, S.~Siuly, and P.~Wen, ``A Hybrid Deep Learning Scheme for Multi-Channel Sleep Stage Classification,'' \emph{Computers, Materials \& Continua}, 2022.
	
	\bibitem{mostafaei2024crossmodality}
	S.~H. Mostafaei, J.~Tanha, and A.~Sharafkhaneh, ``A Novel Deep Learning Model Based on Transformer and Cross-Modality Attention for Classification of Sleep Stages,'' \emph{Journal of Biomedical Informatics}, 2024.
	
	\bibitem{jeong2024explainablevit}
	Jeong et~al., ``Explainable Vision Transformer for Automatic Visual Sleep Staging,'' \emph{npj Digital Medicine}, 2024.
	
	\bibitem{pei2024mfcc}
	W.~Pei, Y.~Li et~al., ``An Automatic Method Using MFCC Features for Sleep Stage Classification,'' \emph{Biomedical Signal Processing and Control}, 2024.
	
	\bibitem{sors2018cnn}
	A.~Sors et~al., ``A Convolutional Neural Network for Sleep Stage Scoring from Raw Single-Channel EEG,'' \emph{Biomedical Signal Processing and Control}, 2018.
	
	\bibitem{seo2020iitnet}
	H.~Seo et~al., ``Intra- and Inter-Epoch Temporal Context Network (IITNet) Using Sub-Epoch Features for Automatic Sleep Scoring on Raw Single-Channel EEG,'' \emph{Biomedical Signal Processing and Control}, 2020.
	
	\bibitem{biswal2017sleepnet}
	S.~Biswal et~al., ``SLEEPNET: Automated Sleep Staging System via Deep Learning,'' \emph{Journal of the American Medical Informatics Association}, 2017.
	
	\bibitem{phan2018jointcnn}
	H.~Phan et~al., ``Joint Classification and Prediction CNN Framework for Automatic Sleep Stage Classification,'' \emph{IEEE Transactions on Biomedical Engineering}, 2018.
	
\end{thebibliography}

